POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2022-06-08 main.tex
add link to the website

\usepackage{graphicx}
\usepackage{cleveref}
\usepackage{natbib}

@@

In recent years, the programming language community has embraced
machine checked proofs for theoretical results in papers. The
POPLMark~\cite{Pierce:2005} challenge was proposed for this purpose,
and to get the community on track. Since then the number of formal
proofs accompanying papers has grown\footnote{add some POPL/PLDI/etc
  statistics here}. However, formal proofs are not equally spread in
the field. In this call to action, we propose to extend the key
contribution of challenges like POPLMark is to help develop the
necessary momentum and culture to be able to formalise results to the
concurrent calculi community by proposing a challenge the exercises
the key aspects of reasoning about process calculi.

@@

As mentioned before, in this work we address another expansion of
scope for such challenges, going from the $\lambda$-calculus to
process calculi such as the $\pi$-calculus and session type systems
(and other behavioural type systems). These systems require particular
insights to implement. So far, we have identified three key
aspects\footnote{We want to keep the number low, but the exact nature
  of the challenges is still open to discussion.}. First, the idea of
scope extrusion in name passing calculi. This generalises the idea of
binders in ways that techniques that were adequate for
$\lambda$-calculus binders are not so convenient for name passing
systems. Second, session types in particular, and behavioural types in
general often depend on linearity in their type systems. The
formalisation of linear type systems posses a challenge given that it
is not uniformly well supported among the many proof assistants.
Finally, processes in concurrent systems often contain infinite
behaviour that is typically modelled with coinduction. This technique
is used to reason about (bi)similarity between processes, the
equivalence of their traces, or subtyping between infinite trees of
possible behaviours. This challenge concentrates on those issues.

>>>>

\usepackage{graphicx}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{cleveref}

@@

In recent years, the programming language community has embraced
machine checked proofs for theoretical results in papers. The
POPLMark~\cite{Pierce:2005} challenge was proposed for this purpose,
and to get the community on track. Since then the number of formal
proofs accompanying papers has grown\footnote{add some POPL/PLDI/etc
  statistics here}. However, formal proofs are not equally spread in
the field. In this call to action, we propose to extend the key
contribution of challenges like POPLMark is to help develop the
necessary momentum and culture to be able to formalise results to the
concurrent calculi community by proposing a challenge the exercises
the key aspects of reasoning about process calculi. We propose this
document, and a \href{https://concurrentbenchmark.github.io/}{website}
to enable the community to collaborate on the project.

@@

As mentioned before, in this work we address another expansion of
scope for such challenges, going from the $\lambda$-calculus to
process calculi such as the $\pi$-calculus and session type systems
(and other behavioural type systems). These systems require particular
insights to implement. So far, we have identified three key
aspects\footnote{We want to keep the number low, but the exact nature
  of the challenges is still open to discussion (as are most things in
  this project).}. First, the idea of scope extrusion in name passing
calculi. This generalises the idea of binders in ways that techniques
that were adequate for $\lambda$-calculus binders are not so
convenient for name passing systems. Second, session types in
particular, and behavioural types in general often depend on linearity
in their type systems. The formalisation of linear type systems posses
a challenge given that it is not uniformly well supported among the
many proof assistants. Finally, processes in concurrent systems often
contain infinite behaviour that is typically modelled with
coinduction. This technique is used to reason about (bi)similarity
between processes, the equivalence of their traces, or subtyping
between infinite trees of possible behaviours. This challenge
concentrates on those issues.
